Assessing Material Inventory Uncertainties in Integrated Fuel Cycle Simulations

### 2018-07-20 paper.tex
review correction

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which calculates the fissile fraction
required in the fuel to reach a given target burnup at the end of irradiation.
Therefore, the uncertainty of the fuel enrichment is not applied directly to the
effective enrichment. It is instead applied to the burnup, resulting in a fuel
enrichment uncertainty that is also close to $10\%$.

@@

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.3]{power_full}
    \caption{Electric power generated as a function of time, wit its uncertainty.}\label{fig:power_full}
\end{figure}

@@

The relative uncertainty of the total uranium consumption starts at about
$7\%$ a slowly drops and stabilize around $3\%$.

Uncertainty fluctuation of the full relative uncertainty can be observed before
year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
beginning of the simulation have synchronized fuel cycles, reloading in the same
time step.  This phenomenon disappears with the gradual decommissioning of the
initial reactors, spread over 50 years.

The decrease of the cycle time uncertainty contribution, from year 30 to year
90, can be understood as an averaging effect.  As the uncertainty are defined
once per deployed facility, each reactor will have a different cycle length
value, so a different number of batches loaded per year.  With the increase of
deployed reactors, the number of batches of \gls{LWR} fuel loaded converges to
the references one, reducing its impact on the uncertainty on the total uranium
consumption. This uncertainty contribution to the overall uncertainty decrease
is proportional to the number of \gls{LWR} reactors and stops with the
decommission of the last one.

@@

It is also interesting to note that, the uncertainty contribution from the cycle
length between year 40 and 70 comes mainly from fuel batch loading frequencies.
After 70 years this contribution follows the thermal power contribution closely,
suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
mechanism of this contribution.

Around the year 70, it is possible to observe the relative uncertainty related
to cycle time being larger than the overall relative uncertainty. This effect is
directly related to the \gls{OFAT} method used to estimate the individual
uncertainty contribution. While allowing a quick access to the individual
contribution, the \gls{OFAT} method does not capture coupling effect between the
different parameters.

@@

Two main points can be deduced from this work.  First, in a transitional fuel
cycle, uncertainty contributions to output metrics can vary over time depending
of various factors: deployment schedule artifacts or material flow
constrictions.

@@

@@

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition.  While it has demonstrated the
capability to measure the uncertainty on output fuel cycle metrics and their
relative contributions, it has only been applied to systematic uncertainties per
facilities.  This kind of study will to be extended to random uncertainty (new
parameter values as a function of time) and completely systematic uncertainty
(shared by all the facilities of a kind).

>>>>

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which calculates the fissile fraction
required in the fuel to reach a given target burnup at the end of irradiation.
The targeted burnup is a operational parameter and does not necessary related to the
actual achieved burnup (computed from the real cycle length and the thermal
power of the reactor). Therefore, the uncertainty of the fuel enrichment is not
applied directly to the effective enrichment. It is instead applied to the
targeted burnup, resulting in a fuel enrichment uncertainty that is also close
to $10\%$.

@@

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.3]{power_full}
    \caption{Electric power generated as a function of time, with its uncertainty.}\label{fig:power_full}
\end{figure}

@@

The relative uncertainty of the total uranium consumption starts at about
$7\%$, slowly droping and stabilizing around $3\%$.

Fluctuation of the full relative uncertainty can be observed before year 50.
Those fluctuation are induced by the fuel loading: all reactors at the beginning
of the simulation have synchronized fuel cycles, reloading in the same time
step.  This phenomenon disappears with the gradual decommissioning of the
initial reactors, spread over 50 years.

The decrease of the cycle time uncertainty contribution, from year 30 to year
90, can be understood as an averaging effect.  As the uncertainty are defined
once per deployed facility, each reactor will have a different cycle length
value, so a different number of batches loaded per year.  With the increase of
deployed reactors, the number of batches of \gls{LWR} fuel loaded converges to
the mean (reference) value, reducing its impact on the uncertainty on the total uranium
consumption. This uncertainty contribution to the overall uncertainty decrease
is proportional to the number of \gls{LWR} reactors and stops with the
decommission of the last one.

@@

The uncertainty contribution from the cycle length between year 40 and 70 comes
mainly from fuel batch loading frequencies (Figure \ref{fig:pu_uncer}.  After 70
years this contribution follows the thermal power contribution closely,
suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
mechanism of this contribution, the variation of cycle length being driving a
direct variation of the burnup as the thermal power is held constant.  \gls{UOX}
Fuel enrichment and separation efficiency showed a relative contribution smaller
than $0.4\%$.

Around the year 70, the relative uncertainty related to cycle time is slightly
bigger than the overall relative uncertainty. This effect is related to the
\gls{OFAT} method used to estimate the individual uncertainty contribution.
While allowing a quick access to the individual contribution, the \gls{OFAT}
method does not capture coupling effect between the different parameters.

@@

Three main points can be deduced from this work.  First, in a transitional fuel
cycle, uncertainty contributions to output metrics can vary over time depending
of various factors: deployment schedule artifacts or material flow
constrictions.

@@

Finally, Figure \ref{fig:pu_uncer} shows the limit of the \gls{OFAT} method to
assess the individual contribution of each parameter, missing all the coupling
effect between each of them...

@@

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition.  While it has demonstrated the
capability to measure the uncertainty on output fuel cycle metrics and their
relative contributions, it has only been applied to systematic uncertainties per
facilities.  This kind of study will to be extended to random uncertainty (new
parameter values as a function of time) and completely systematic uncertainty
(shared by all the facilities of a kind). Additionally more sophisticated methods needs to
be used to assess precisely each parameter contributions..
